---
title: "MM_3_DataSimulation"
author: '11175615'
date: "2023-02-20"
output: html_document
---

## Workshop code

```{r}
library(tidyverse)
library(broom)
```




### 1. Simulate data for n = 200

```{r}
total_samples <- 200
sample_size <- 24
participant <- rep(1 : sample_size)
condition <- c(rep("fast", times = sample_size/2),
               rep("slow", times = sample_size/2))

all_data <- NULL

for (i in 1: total_samples) {
  sample <- i
  set.seed(1233+i)
  dv <- c(rnorm(sample_size/2, 1000,50), 
          rnorm(sample_size/2, 1020, 50))
  my_data <- as_tibble(cbind(participant, condition, dv, sample))
  all_data <- rbind(my_data, all_data)
}

all_tidied_data <- all_data %>%
  mutate(condition = factor(condition),
         dv = as.integer(dv))

```


Can you detect a statistically significant difference?

```{r}
result <- NULL
for (i in 1:total_samples) {
  result <- rbind(tidy(t.test(filter(all_tidied_data, 
                                     condition == "fast" & sample == i)$dv,
                              filter(all_tidied_data, 
                                     condition == "slow" & sample == i)$dv,
                              paired = FALSE)), result)
}

result


result %>% 
  filter(p.value < .05) %>%
  count()
```


Repeating with variation in the standard deviations. 

```{r}
total_samples <- 200
sample_size <- 24
participant <- rep(1 : sample_size)
condition <- c(rep("fast", times = sample_size/2),
               rep("slow", times = sample_size/2))

all_data <- NULL

for (i in 1: total_samples) {
  sample <- i
  set.seed(1233 + i)
  dv <- c(rnorm(sample_size/2, 1000,200), 
          rnorm(sample_size/2, 1020, 50))
  my_data <- as_tibble(cbind(participant, condition, dv, sample))
  all_data <- rbind(my_data, all_data)
}


all_tidied_data <- all_data %>%
  mutate(condition = factor(condition),
         dv = as.integer(dv))


result <- NULL
for (i in 1:total_samples) {
  result <- rbind(tidy(t.test(filter(all_tidied_data, 
                                     condition == "fast" & sample == i)$dv,
                              filter(all_tidied_data, 
                                     condition == "slow" & sample == i)$dv,
                              paired = FALSE)), result)
}

result


result %>% 
  filter(p.value < .05) %>%
  count()
```


Looking at effect size using Cohen's

```{r}
(1020-1000)/(50)


(1020-1000)/(50)
```


### 2. How many subjects would you need for a difference of 40ms

New effect size: 

```{r}
(40)/(50)
```


Power analysis: 

```{r}
library(pwr)

pwr.t.test(d = 0.8, sig.level = 0.05, power = 0.8, type = c("two.sample"))

pwr.t.test(n = 25.5, sig.level = 0.05, power = 0.8, type = c("two.sample"))
```



### 3. Running the loop with ANOVA instead of t-tests

Using repeated measures as participants repeat.

**couldn't get the code to work - going to add this when I can!**





